The pollination trade-off

### 2019-04-09 paper/manuscript.Rmd
Move keywords to title page
Other edits to title page re. author information

@@

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE, dpi = 300)
# library(magrittr)
# library(foreach)
# library(drake)
# # load functions
# f <- lapply(list.files("../code", full.names = T), source)
```
```

@@

**Keywords:** X, Y, Z

>>>>

**Keywords:** X,Y,Z

**Type of article:** Letter

@@

**Author for correspondence:** E. Fernando Cagua (efc29@uclive.ac.nz) - +64 20 4026 8153

**Authors' email addresses:** Hugo J. Marrrero (hugomarrero@gmail.com); Jason M. Tylianakis (jason.tylianakis@canterbury.ac.nz); Daniel B. Stouffer (daniel.stouffer@canterbury.ac.nz)

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE, dpi = 300)
```

@@
